---
title: "old faithful"
author: "Jack Martin"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The Old Faithful data set contains the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Tellowstone National Parkm Wyoming, USA.

```{r, load dataframe} 
df <- faithful 
```


The data description is fiven in the table below. 

|Variable        |Description                            | 
|----------------|---------------------------------------|
|eruptions       |  the duration of the eruption, minutes|
|waiting	       | waiting time to next eruption, minutes|

A summary of the distributions of each variable are as follows

``` {r summary} 
    summary(df)
```

The marginal distributions of the variable shown below:

``` {r}
hist(df$eruptions)
```

``` {r}
hist(df$waiting)
```

# Conclusions and Further Work

Both the duration of eruptions and waiting time show a bimodal distribution. In further work I will plot the scatter of the data (‘eruptions duration’ vs ‘waiting time’ ) to see whether I can detect any patterns